COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
imported questionnaire data and prepared hypothesis 1c

@@

@@

>>>>

  # import questionnaire data from RedCap

  data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)

@@

      # make a temporary copy of the rt data frame without 1-back

@@

```{r Hypothesis_1c, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

  # H1c: Ratings on all NTLX dimensions increase with increasing n-back level.

  # aggregate NTLX data per participant per level

  data_ntlx <- data.frame(subject = character(), level = double(),
                          mental = double(), physical = double(), time = double(),
                          performance = double(), effort = double(), frustration = double())

  # six ANOVAs with six linear contrasts, contrasting the subscale scores of two n-back levels (1,2,3,4) at a time

      # make a temporary copy of the NTLX data frame

      h3a_data <- data_ntlx
      h3a_data$level <- as.factor(h3a_data$level)

      contrasts(h3a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                         c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))

      # calculate ANOVAs

      hypothesis3a1_anova <- summary(aov(h3a_data$mental ~ h3a_data$level))
      hypothesis3a1_posthoc <- TukeyHSD(aov(h3a_data$mental ~ h3a_data$level))

      hypothesis3a2_anova <- summary(aov(h3a_data$physical ~ h3a_data$level))
      hypothesis3a2_posthoc <- TukeyHSD(aov(h3a_data$physical ~ h3a_data$level))

      hypothesis3a3_anova <- summary(aov(h3a_data$time ~ h3a_data$level))
      hypothesis3a3_posthoc <- TukeyHSD(aov(h3a_data$time ~ h3a_data$level))

      hypothesis3a4_anova <- summary(aov(h3a_data$performance ~ h3a_data$level))
      hypothesis3a4_posthoc <- TukeyHSD(aov(h3a_data$performance ~ h3a_data$level))

      hypothesis3a5_anova <- summary(aov(h3a_data$effort ~ h3a_data$level))
      hypothesis3a5_posthoc <- TukeyHSD(aov(h3a_data$effort ~ h3a_data$level))

      hypothesis3a6_anova <- summary(aov(h3a_data$frustration ~ h3a_data$level))
      hypothesis3a6_posthoc <- TukeyHSD(aov(h3a_data$frustration ~ h3a_data$level))

      remove(h3a_data)
